Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
Acknowledge grants
More humble statement in discussion of model-based approaches

% RSC + LOC
Apart from the PPA, results revealed significantly increased activity in the
dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
RSC) and lateral occipital cortex (LOC; more lateral in the movie stimulus, more
medial in the audio-description stimulus) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly showed increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our approach to operationalize spatial perception based on stimulus
annotations did not lead to significant clusters scattered across the brain but
restricted to a brain network that is assumed/known to be involved in (visual)
spatial perception and cognition.
%
This suggest that model-driven methods based on stimulus annotations are
suitable to reveal spatially concise functional areas and networks.
%
Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
to noise-cluster ration)\todo{if you know what I mean} depends on how many
events correlating with an assumed perceptual process the stimulus provides and
to the extent to which a naturalistic stimulus' multi-dimensionality is
annotated and statistically controlled.

@@

>>>>

% RSC + LOC
Apart from the PPA, results show significantly increased activity in the
dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
RSC) and lateral occipital cortex (LOC; more lateral in the movie stimulus, more
medial in the audio-description stimulus) for both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our model-driven approach to operationalize spatial perception based on stimulus
annotations reveals focussed activation patterns in networks that are implicated
in visual spatial perception and cognition.

@@

This research was, in part, supported by the German Federal Ministry of
Education and Research (BMBF, 01GQ1112) and the US National Science Foundation
(NSF, 1129855). Work on the data-sharing technology employed for this research
was supported by BMBF (01GQ1411, 01GQ1905) and NSF (1429999, 1912266).
